\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-12-07 flux.tex
Fix #36 - Ne*tau estimates.

%%% trees %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=0.85\textwidth]{figures/trees}
	\caption{\textbf{Time-resolved phylogenetic trees of A/H3N2, A/H1N1, B/Vic and B/Yam viruses.} 
	The maximium-clade credibility (MCC) tree is shown for each virus.
	These trees show genealogical relationships, so that branches are measured in terms of years rather than substitutions.
	The mean posterior scaled effective population size $N_e \tau$, measured in years, and its 95\% credible interval is shown for each virus.} 
	\label{trees} 
\end{figure}

>>>>

%%% trees %%%
\begin{figure}[h]
	\centering		
	\includegraphics[width=0.85\textwidth]{figures/trees}
	\caption{\textbf{Time-resolved phylogenetic trees of A/H3N2, A/H1N1, B/Vic and B/Yam viruses.} 
	The maximium-clade credibility (MCC) tree is shown for each virus.
	These trees show genealogical relationships, so that branches are measured in terms of years rather than substitutions.} 
	\label{trees} 
\end{figure}
